### 2023-01-24 article.tex
Correct singular/plurality

In this paper, the definition of paradata
is 'information about how data was generated',
as shown schematically in the left panel of Figure \ref{fig:figure_1}.
Paradata does not have a clear definition yet (hence this book). 
Common elements in the definitions of paradata are 
(1) paradata are usually not the primary data, (2) paradata describe
a process, (3) paradata describe the way of collecting primary data, or 
(4) paradata describe the way the primary data is generated.

@@

Here are multiple suggestions to make containers with runnable code FAIR.
To make such containers findable, the most common 
environments (Syslabs and DockerHub) to upload containers must be indexed.
Uploading a container to those environments is, however, limited by
a restricted amount of free storage, with the possible consequence that
those containers are uploaded somewhere where they escape proper indexing.
Having containers uploaded at the existing websites ensures they are
accessible, interoperable and reusable.
One could argue however, that the scientific community need its own,
similar website to upload containers, as the metadata for these
sites are limited to free-text comments and tags (DockerHub)
or not metadata at all (Syslabs).

>>>>

In this paper, the definition of paradata
is 'information about how data was generated',
as shown schematically in the left panel of Figure \ref{fig:figure_1}.
Paradata does not have a clear definition yet (hence this book). 
Common elements in the definitions of paradata are 
(1) paradata is usually not the primary data, (2) paradata describes
a process, (3) paradata describes the way of collecting primary data, or 
(4) paradata describes the way the primary data is generated.

@@

Here are multiple suggestions to make containers with runnable code FAIR.
To make such containers findable, the most common 
environments (Syslabs and DockerHub) to upload containers must be indexed.
Uploading a container to those environments is, however, limited by
a restricted amount of free storage, with the possible consequence that
those containers are uploaded somewhere where they escape proper indexing.
Having containers uploaded at the existing websites ensures they are
accessible, interoperable and reusable.
One could argue however, that the scientific community need its own,
similar website to upload containers, as the metadata for these
sites is limited to free-text comments and tags (DockerHub)
or not metadata at all (Syslabs).
